---
title: "Survey 3: Data Simulation (coding/scoring)"
format: html
editor: visual
---

This document includes the code to simulate a dataset for Survey 3 of Wave 1 of the Explaining Atheism project.

Survey 3 includes the Socialisation cluster of variables, along with some response variables. We will generate the dataset with our custom easim function.

## Load packages and functions

Here we load dyplr, and our custom function. We use groundhog for reproducibility

```{r}

library(groundhog)

libs <- c("dplyr", "stringr")

groundhog.library(libs, "2023-09-23")


source("../../../../funs/datasim.R")

easim <- easim_odd  #to overwrite the easim we loaded with the easim_odd (so we get alternating cols) rather than changing all the code below to easim_odd. We can change this depending on what data type we want. See datasim.R.


set.seed(1993)
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "Japan", "UK"),
                                  100,
                                  replace = TRUE))
```

## CREDs

The creds scale has a series of different response options, some not standard, so we need to specify these separately.

### Specify response scales

#### 

```{r}
sincerity <- c("Completely Insincere",
               "Very Insincere",
               "Insincere",
               "Neutral",
               "Sincere",
               "Very Sincere",
               "Completely Sincere")

```

*cred_01:06*

These use the same scale so we can use easim_odd

```{r}

df <- easim_odd(df, 6, "cred_", "extent", 700)
```

*cred_07* has yes/no responses

```{r}


df <- easim_odd(df, 7, "cred_", "yesno", 700, NULL,  7)
```

*cred_09*

```{r}

df <- easim_odd(df, 9, "cred_", "yesno", 700, NULL, 9)
```

*cred_10*

```{r}

df <- easim_odd(df, 10, "cred_", "custom", 700 , sincerity, 10)

```

*cred_11*

```{r}

df <- easim_odd(df, 11, "cred_", "extent", 700, NULL, 11)
```

*cred_12*

```{r}

df <- easim_odd(df, 12, "cred_", "custom", 700, sincerity, 12)
```

*cred_13, cred_14*

```{r}
df <- easim_odd(df, 14, "cred_", "extent", 700, NULL, 13)

```

*cred_15*

```{r}
df <- easim_odd(df, 15, "cred_", "frequency", 700, NULL, 15)
```

*cred_16*

```{r}
df <- easim_odd(df, 16, "cred_", "extent", 700, NULL, 16)
```

cred_17:25

```{r}

df$cred_18 <- df$cred_09

df$cred_19 <- df$cred_10

df$cred_20 <- df$cred_11

df$cred_21 <- df$cred_12

df$cred_22 <- df$cred_13

df$cred_23 <- df$cred_14

df$cred_24 <- df$cred_15

df$cred_25 <- df$cred_16

```

*cred_27*

```{r}
df <- easim_odd(df, 27, "cred_", "extent", 700, NULL, 27)
```

*cred_28*

```{r}
df <- easim_odd(df, 28, "cred_", "custom", 700, sincerity, 28)
```

*cred_30*

```{r}
df <- easim_odd(df, 30, "cred_", "extent", 700, NULL, 30)
```

*cred_31*

```{r}
df <- easim_odd(df, 31, "cred_", "custom", 700, sincerity, 31)
```

## CRUDs

```{r}

df <- easim_odd(df, 3, "crud_",  "extent", 700)

```

## Non-theistic Socialisation

```{r}

df <- easim_odd(df, 8, "nts_",  "extent", 700)

```

#Normativity of Religion

```{r}
df <- easim_odd(df, 12, "norm_",  "extent", 700)

```

## Religious Emphasis

```{r}

df <- easim_odd(df, 9, "re_",  "extent", 700)

```

## Parental Circumstances


```{r}

df <- easim_odd(df,
                1, 
                "pc_", 
                "custom",
                700, 
                c("Living with own mother and father",
                  "Living with two mothers",
                  "Living with two fathers",
                  "Living with own father and stepmother",
                  "Living with own mother and stepfather",
                  "Living with own father only",
                  "Living with own mother only",
                  "Living with other relatives",
                  "Don't Know",
                  "Other (please specify)"),
                1)

df <- easim_odd(df,
                2, 
                "pc_", 
                "custom", 
                700,
                c("Mother deceased",
                  "Father deceased",
                  "Both parents deceased",
                  "Parents divorced or separated",
                  "Father absent (e.g. armed forces, institution)",
                  "Mother absent (e.g. armed forces, institution)",
                  "Both parents absent (e.g. armed forces)",
                  "Other (please specify)", "Don’t know"),
                2)



```




## Belief Measure Variables

### ISSP

As there is no reverse coding we can again use normal easim

```{r}

df <- easim(df,
            1,
            "issp_",
            "custom",
            700,
            custom = c("I don't believe in God",
                       "I don't know whether there is a God, and I don't believe there is any way to find out",
                       "I don't believe in a personal God, but I do believe in a Higher Power of some kind",
                       "I find myself believing in God some of the time, but not at others",
                       "While I have doubts, I feel that I do believe in God.",
                       "I know God really exists and I have no doubt about it.",
                       "Don't know"
                       ))

df <- easim(df,
            2,
            "issp_",
            "custom",
            700,
            custom = c("Spiritual but not religious",
                       "Seeker",
                       "Non-religious",
                       "Atheist",
                       "Agnostic",
                       "Humanist",
                       "Sceptic",
                       "Free thinker",
                       "Rationalist",
                       "Secular",
                       "Christian",
                       "Muslim",
                       "Jewish",
                       "Buddhist",
                       "Hindu",
                       "Daoist",
                       "Shinto",
                       "Confucian",
                       "Other (please specify)"
            ), 
            2)

```

### Religious Identity

```{r}

df <- easim(df, 1, "rid_", "yesno", 700)

df <- easim(df,
            2,
            "rid_",
            "custom",
            700,
            c("Protestant",
              "Catholic",
              "Orthodox (e.g. Greek Orthodox, Russian Orthodox)",
              "Sunni",
              "Shiite",
              "Buddhist",
              "Confucian",
              "Daoist",
              "Hindu",
              "Jewish",
              "Shinto",
              "Other (please specify)"),
            2)


```

### Religious Practice

```{r}

df <- easim(df,
            1,
            "rp_",
            "custom",
            700,
            c("More than once a week",
              "Once a week",
              "Once a month",
              "Only on special holy days",
              "Once a year",
              "Less often",
              "Never, practically never"
            ),
            1)


df <- easim(df,
            2,
            "rp_",
            "custom",
            700,
            c("Several times a day",
              "Once a day",
              "Several times each week",
              "Only when attending religious services",
              "Only on special holy days",
              "Once a year",
              "Less often",
              "Never, practically never"
            ),
            2)


df <- easim(df,
            3,
            "rp_",
            "custom",
            700,
            c("Yes, for religious reasons",
              "Yes, for non-religious reasons",
              "No"),
            3)

```

### Supernatural Belief

```{r}

df <- easim(df, 15, "snb_", "agreement", 700)

df <- easim(df, 16, "snb_", "custom", 700, c("Yes, I’ve had an experience like this.",
                                            "I’ve had an experience like this, but I didn’t associate it with a spiritual force.",
                                            "No, I’ve never had an experience like this."),
            16)

df <- easim(df, 17, "snb_", "yesno", 700, NULL,  17)


```

### General Belief

```{r}

df <-  easim(df, 2, "belief_", "agreement", 700)

df <-  easim(df, 1, "conf_", "agreement", 700)

df <-  easim(df, 1, "ar_", "agreement", 700)

df <-  easim(df, 2, "apth_", "agreement", 700)

df <-  easim(df, 1, "mean_", "agreement", 700)

df <-  easim(df, 1, "agn_", "agreement", 700)


```

### Atheist Membership

```{r}

df <- easim(df, 1, "am_", "yesno", 700)
```

## Write Datafile

```{r}
write.csv(df, "survey3_testdat_sc.csv", row.names = TRUE)
```
