---
title: "Survey 3 Coding + Scoring"
format: html
editor: visual
---

The first part of this file codes the raw survey responses. The second part scores these into our final variables.

### Load packages, function, and data

```{r}

library(groundhog)

libs <- c("dplyr", "stringr")

groundhog.library(libs, "2023-09-23")

#load functions   
#these function requires some tidyverse elements 

source("../../funs/scoringFuns.R")

source( "../../funs/beliefcodeFun.R")
source( "../../funs/beliefscoreFun.R")


```

#### Data

```{r}
getwd() 

survey3 <- read.csv("../data/fake_data/for_scoring_coding/survey3_testdat_sc.csv")

```

# Part 1 - Coding Survey Responses

## Socialisation

### CREDs

```{r}

#first specify extent cols

cred_extent <- c("01", "02", "03", "04", "05", "06", "11", "13", "14", "16", "20", "22", "23", "25", "27", "30")
cred_extent <- paste0("cred_", cred_extent)


cred_yesno <- c("07", "09", "18")
cred_yesno <- paste0("cred_", cred_yesno)


cred_freq <- c("15", "24")
cred_freq <- paste0("cred_", cred_freq)


cred_sincere <- c("10", "12", "19", "21", "28", "31")
cred_sincere <- paste0("cred_", cred_sincere)



survey_3_coded <- funScore(survey3, cred_extent, "extent", FALSE)

survey_3_coded <- funScore(survey_3_coded, cred_freq, "frequency", FALSE)

survey_3_coded <- funScore(survey_3_coded, cred_sincere, "custom", FALSE,
                           custom = c(
                             "Completely Insincere",
                             "Very Insincere",
                             "Insincere",
                             "Neutral",
                             "Sincere",
                             "Very Sincere",
                             "Completely Sincere"
                           ))

survey_3_coded <- funScore(survey_3_coded, cred_yesno, "yesno", FALSE)

```

### CRUDs

```{r}

cruds <- colnames(survey_3_coded %>% select(starts_with("crud_")))

survey_3_coded <- funScore(survey_3_coded, cruds, "extent", FALSE)

```

### Non-theistic Socialisation

```{r}

nts <- colnames(survey_3_coded %>% select(starts_with("nts_")))

survey_3_coded <- funScore(survey_3_coded, nts, "extent", FALSE)

```

### Normativity

```{r}

norm <- colnames(survey_3_coded %>% select(starts_with("norm_")))

survey_3_coded <- funScore(survey_3_coded, norm, "extent", FALSE)

```

### Religious Emphasis

```{r}

emph <- colnames(survey_3_coded %>% select(starts_with("re_")))

survey_3_coded <- funScore(survey_3_coded, emph, "extent", FALSE)

```

### Paraental Circumstances

No coding.

## Belief Measures

We have a function for these!

```{r}

survey_3_coded <- funBeliefCode(survey_3_coded)

```

## Write coded data

```{r}

write.csv(survey_3_coded, "survey_3_coded_FAKE.csv", row.names = FALSE)
```

# Part 2 - Scoring Survey Variables

Here we score the needed columns into the final variables, and rename the questions to their variable names if needed.

```{r}

# Cognitive Styles Variables

survey_3_scored <- survey_3_coded %>%
  mutate(
    #CRUD (caregiver)
    cred_caregiver = rowMeans(across(c("cred_01", "cred_02", "cred_03", "cred_04", "cred_05", "cred_06"))), 
    
    #CRED (group leader)
    cred_grp_leader = rowMeans(across(c("cred_10", "cred_11", "cred_19", "cred_20"))), 
    
    #CRED (group member)
    cred_grp_mbr = rowMeans(across(c("cred_12", "cred_13", "cred_14", "cred_15", "cred_16", "cred_21", "cred_22", "cred_23", "cred_24"))),
    
    #CRED (group)
    
    cred_grp = rowMeans(across(c("cred_grp_mbr", "cred_grp_leader"))),
    
    #CRED Exposure
    
    cred = rowMeans(across(c("cred_grp", "cred_caregiver"))),
    
    #CRUD (caregiver)
    
    crud_caregiver = crud_01, 
    
    #CRUD (group member)
    
    crud_grp_mbr = crud_02,
    
    #CRUD (group leader)
    
    crud_grp_ldr = crud_03, 
    
    #CRUD (group)
    
    crud_grp = rowMeans(across(c("crud_grp_mbr", "crud_grp_ldr"))),
    
    #CRUD
    
    crud = rowMeans(across(c("crud_grp", "crud_caregiver"))),
    
    #Non-theistic Socialisation
    
    nontheistic_soc = rowMeans(across(starts_with("nts_"), ~ as.numeric(.))),
    
    #Normativity of Religion
    
    normativity = rowMeans(across(starts_with("norm_"), ~ as.numeric(.))),
    
    #Normativity of Religion (Nation)
    
    normativity_nat = rowMeans(across(c("norm_01", "norm_02", "norm_03"))),

    #Normativity of Religion (Ethnicity)
    
    normativity_eth = rowMeans(across(c("norm_04", "norm_05", "norm_06"))),    
    
    #Normativity of Religion (Peers)
    
    normativity_peer = rowMeans(across(c("norm_07", "norm_08", "norm_09"))),    
    
    #Normativity of Religion (Group)
    
    normativity_grp = rowMeans(across(c("norm_10", "norm_11", "norm_12"))),
    
    #Religious Emphasis
    
    relig_emph = rowMeans(across(starts_with("re_"), ~ as.numeric(.))),
    
    #Parental Circumstances
    
    parental_circ = pc_01, 
    
    #Parental Absence Reason
    
    parent_absence = pc_02)


# Belief measures

survey_3_scored <- funBeliefScore(survey_3_scored)

```

## Write scored data

```{r}

write.csv(survey_3_scored, "survey_3_scored_FAKE.csv", row.names = FALSE)
```

## Select Variables

```{r}

survey_3_vars <- survey_3_scored %>%
  select(1, 2, 3, 4, 100:157, -apx1, -apx2)

```

## Write variable data

```{r}

write.csv(survey_3_vars, "survey_3_vars_FAKE.csv", row.names = FALSE)
```


