---
title: "Cognitive Bias Testing Data"
format: html
---

Here we create a dataframe for testing our scoring functions. Each odd column for each scale will be reversed, to allow easy visual inspection.

We could also use easim to get random samples for each response sequence as an additional check.


#### Load packages and functions


```{r}
library(tidyverse)
source("datasim.R")
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "China", "Denmark", "Japan", "UK", "USA"), 100, replace = TRUE))
```

## Anthropomorphism

```{r}
df <- easim_odd(df, 10, "anth_", "agreement", 700)

```

## Mentalizing

```{r}

df <- easim_odd(df, 22, "mnt_", "custom" , 700, c("Definitely Disagree", "Slightly Disagree", "Slightly  Agree", "Definitely  Agree"))

```

## Dualism

```{r}

df <- easim_odd(df, 10, "dua_", "agreement", 700)

```

## Pattern Perception

```{r}

df <- easim_odd(df, 11, "pp_", "custom", 700, c("Completely Random", 
                                                "Very Random", 
                                                "Fairly Random", 
                                                "Unsure Whether Random Or Non-Random", 
                                                "Fairly Non-Random", 
                                                "Very Non-Random", 
                                                "Completely Non-Random"))

```

## Promiscuous Teleology

```{r}

df <- easim_odd(df, 14, "tel_", "agreement", 700)

```

## Schizotypy


```{r}

df <- easim_odd(df, 18, "sz_", "yesno", 700)

```

## Vividness of Mental Imagery

```{r}

df <- easim_odd(df, 32, "vvi_", "custom", 700, c( "Perfectly clear and as vivid as normal vision", 
                                                  "Clear and reasonably vivid", 
                                                  "Moderately clear and vivid", 
                                                  "Vague and dim", 
                                                  "No image at all, you only 'know' that you are thinking of an object"
  
))
```

##  Write file

```{r}

write.csv(df, "cogbias_testdat.csv")

```




