---
title: "Cognitive Style Testing Data"
format: html
---

Here we create a dataframe for testing our scoring functions. Each odd column for each scale will be reversed, to allow easy visual inspection.

We could also use easim to get random samples for each response sequence as an additional check.

#### Load packages and functions


```{r}
library(tidyverse)
source("datasim.R")
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "China", "Denmark", "Japan", "UK", "USA"), 100, replace = TRUE))
```

## Tolerance of  Ambiguity

```{r}
df <- easim_odd(df, 13, "at_", "agreement", 700)
```

## Thinking Style

## Non-verbal  Reasoning

## Moralisation  of Rationality

```{r}
df <- easim_odd(df, 9, "mor_", "agreement", 700)

```

## Importance of Rationality

```{r}

df <- easim_odd(df, 6, "imp_", "agreement", 700)

```
## Write File

```{r}
write.csv(df, "cogstyle_testdat.csv")
```


