---
title: "Motivational Testing Data"
format: html
---

Here we create a dataframe for testing our scoring functions. Each odd column for each scale will be reversed, to allow easy visual inspection.

We could also use easim to get random samples for each response sequence as an additional check.


#### Load packages and functions


```{r}
library(tidyverse)
source("datasim.R")
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "China", "Denmark", "Japan", "UK", "USA"), 100, replace = TRUE))
```

## Social Desirability

```{r}

df <- easim_odd(df, 8, "sd_", "truth", 700)

```

## Existential Security

```{r}

df <- easim_odd(df,  21,  "es_", "frequency", 700)


df <- easim_odd(df, 3, "ss_", "agreement", 700)

df <- easim_odd(df, 3, "wi_", "agreement", 700)

df <- easim_odd(df, 3, "st_", "agreement", 700)


```

## Need for Structure

```{r}

df <- easim_odd(df, 12, "nfs_", "agreement", 700)

```

## Death Anxiety


```{r}

df <- easim_odd(df, 12, "da_", "agreement", 700)

```

## Social Network Size

```{r}

```

## Need for Meaning

```{r}

df <- easim_odd(df, 10, "mlq_", "truth", 700)

df <- easim_odd(df, 10, "nfm_", "agreement", 700)

```

## Disgust Sensitivity

```{r}

df <- easim_odd(df, 13, "ds_", "truefalse", 700)

df <- easim_odd(df, 25, "ds_", "custom", 700,
              custom =c("Not Disgusting",
                        "Slightly Disgusting",
                        "Very Disgusting"),
              qns= 14)

```

## Write data

```{r}
write.csv(df,  "motiv_testdat.csv")
```



