---
title: "Socialisation Testing Data"
format: html
---

Here we create a dataframe for testing our scoring functions. Each odd column for each scale will be reversed, to allow easy visual inspection.

We could also use easim to get random samples for each response sequence as an additional check.


#### Load packages and functions


```{r}
library(tidyverse)
source("datasim.R")
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "China", "Denmark", "Japan", "UK", "USA"), 100, replace = TRUE))
```


## CREDs

The creds scale has a series of different response options, some not standard, so we need to specify these separately.

### Specify response  scales

```{r}


yesno <- c("Yes", "No")

sincerity <- c("Completely Insincere",
               "Very Insincere",
               "Insincere",
               "Neutral",
               "Sincere",
               "Very Sincere",
               "Completely Sincere")

extent <- c("1 - To No Extent At All",
            "2",
            "3",
            "4",
            "5",
            "6",
            "7 - To a Great Extent")

frequency <- c("Never",
               "Very Infrequently",
               "Infrequently",
               "Sometimes",
               "Frequently",
               "Very Frequently",
               "Always")

```


*cred_01:06*

These use the same scale so we can use easim_odd

```{r}

df <- easim_odd(df, 6, "cred_", "agreement", 700)
```


*cred_07* has yes/no responses

```{r}
df$cred_07 <- rep(yesno)

```

*cred_09*

```{r}

df$cred_09 <- rep(yesno)

```

*cred_10*

```{r}

df$cred_10 <- rep(sincerity)

```

*cred_11*

```{r}

df$cred_11 <- rep(extent)

```

*cred_12*

```{r}

df$cred_12 <- rep(sincerity)

```

*cred_13,  cred_14*

```{r}
df$cred_13 <- rep(extent)

df$cred_14 <- rep(extent)

```

*cred_15*

```{r}
df$cred_15 <- rep(frequency)
```


```{r}
df$cred_16 <- rep(extent)
```

*cred_27*

```{r}
df$cred_27 <- rep(extent)
```

*cred_28*

```{r}
df$cred_28 <- rep(sincerity)
```

*cred_30*

```{r}
df$cred_30 <- rep(extent)

```

*cred_31*

```{r}
df$cred_31 <- rep(sincerity)
```

## CRUDs

```{r}

df <- easim_odd(df, 3, "crud_",  "extent", 700)

```

##  Non-theistic Socialisation

```{r}

df <- easim_odd(df, 8, "nts_",  "extent", 700)

```

#Normativity of Religion

```{r}
df <- easim_odd(df, 12, "norm_",  "extent", 700)

```

## Religious Emphasis

```{r}

df <- easim_odd(df, 9, "re_",  "extent", 700)

```


## Write file

```{r}

write.csv(df, "soc_testdat.csv")

```



