---
title: "Survey 4: Data Simulation (coding/scoring)"
format: html
editor: visual
---

This document includes the code to simulate a dataset for Survey 4 of Wave 1 of the Explaining Atheism project.

Survey 4 includes the Motivational cluster of variables, along with some response variables. We will generate the dataset with our custom easim function.

## Load packages and functions

Here we load dyplr, and our custom function. We use groundhog for reproducibility

```{r}

library(groundhog)

libs <- c("dplyr", "stringr")

groundhog.library(libs, "2023-09-23")

source("../../../../funs/datasim.R")

easim <- easim_odd  #to overwrite the easim we loaded with the easim_odd (so we get alternating cols) rather than changing all the code below to easim_odd

set.seed(1993)
```

## Create df and demographics

```{r}
# data frame with ID, Sex, and Age variables
df <- data.frame(ID = 1:700,
                 sex = sample(c("Male", "Female"), 100, replace = TRUE),
                 age = round(rnorm(100, mean = 30, sd = 10)), 
                 country = sample(c("Brazil", "Japan", "UK"),
                                  100,
                                  replace = TRUE))
```

## Social Desirability

```{r}

df <- easim_odd(df, 8, "sd_", "truth", 700)

```

## Existential Security

```{r}

df <- easim_odd(df,  21,  "es_", "frequency", 700)


df <- easim_odd(df, 3, "ss_", "agreement", 700)

df <- easim_odd(df, 3, "wi_", "agreement", 700)

df <- easim_odd(df, 3, "st_", "agreement", 700)


```

## Need for Structure

```{r}

df <- easim_odd(df, 12, "nfs_", "agreement", 700)

```

## Death Anxiety

```{r}

df <- easim_odd(df, 12, "da_", "agreement", 700)

```

## Social Network Size

```{r}

```

## Need for Meaning

```{r}

df <- easim_odd(df, 10, "mlq_", "truth", 700)

df <- easim_odd(df, 10, "nfm_", "agreement", 700)

```

## Disgust Sensitivity

```{r}

df <- easim_odd(df, 13, "ds_", "truefalse", 700)

df <- easim_odd(df, 25, "ds_", "custom", 700,
              custom =c("Not disgusting",
                        "Slightly disgusting",
                        "Very disgusting"),
              qns= 14)

```

## Belief Measure Variables

### ISSP

As there is no reverse coding we can again use normal easim

```{r}

df <- easim(df,
            1,
            "issp_",
            "custom",
            700,
            custom = c("I don't believe in God",
                       "I don't know whether there is a God, and I don't believe there is any way to find out",
                       "I don't believe in a personal God, but I do believe in a Higher Power of some kind",
                       "I find myself believing in God some of the time, but not at others",
                       "While I have doubts, I feel that I do believe in God.",
                       "I know God really exists and I have no doubt about it.",
                       "Don't know"
                       ))

df <- easim(df,
            2,
            "issp_",
            "custom",
            700,
            custom = c("Spiritual but not religious",
                       "Seeker",
                       "Non-religious",
                       "Atheist",
                       "Agnostic",
                       "Humanist",
                       "Sceptic",
                       "Free thinker",
                       "Rationalist",
                       "Secular",
                       "Christian",
                       "Muslim",
                       "Jewish",
                       "Buddhist",
                       "Hindu",
                       "Daoist",
                       "Shinto",
                       "Confucian",
                       "Other (please specify)"
            ), 
            2)

```

### Religious Identity

```{r}

df <- easim(df, 1, "rid_", "yesno", 700)

df <- easim(df,
            2,
            "rid_",
            "custom",
            700,
            c("Protestant",
              "Catholic",
              "Orthodox (e.g. Greek Orthodox, Russian Orthodox)",
              "Sunni",
              "Shiite",
              "Buddhist",
              "Confucian",
              "Daoist",
              "Hindu",
              "Jewish",
              "Shinto",
              "Other (please specify)"),
            2)


```

### Religious Practice

```{r}

df <- easim(df,
            1,
            "rp_",
            "custom",
            700,
            c("More than once a week",
              "Once a week",
              "Once a month",
              "Only on special holy days",
              "Once a year",
              "Less often",
              "Never, practically never"
            ),
            1)


df <- easim(df,
            2,
            "rp_",
            "custom",
            700,
            c("Several times a day",
              "Once a day",
              "Several times each week",
              "Only when attending religious services",
              "Only on special holy days",
              "Once a year",
              "Less often",
              "Never, practically never"
            ),
            2)


df <- easim(df,
            3,
            "rp_",
            "custom",
            700,
            c("Yes, for religious reasons",
              "Yes, for non-religious reasons",
              "No"),
            3)

```

### Supernatural Belief

```{r}

df <- easim(df, 15, "snb_", "agreement", 700)

df <- easim(df, 16, "snb_", "custom", 700, c("Yes, I’ve had an experience like this.",
                                            "I’ve had an experience like this, but I didn’t associate it with a spiritual force.",
                                            "No, I’ve never had an experience like this."),
            16)

df <- easim(df, 17, "snb_", "yesno", 700, NULL,  17)


```

### General Belief

```{r}

df <-  easim(df, 2, "belief_", "agreement", 700)

df <-  easim(df, 1, "conf_", "agreement", 700)

df <-  easim(df, 1, "ar_", "agreement", 700)

df <-  easim(df, 2, "apth_", "agreement", 700)

df <-  easim(df, 1, "mean_", "agreement", 700)

df <-  easim(df, 1, "agn_", "agreement", 700)

```

### Atheist Membership

```{r}

df <- easim(df, 1, "am_", "yesno", 700)
```

## Write Datafile

```{r}
write.csv(df, "survey4_testdat_sc.csv", row.names = FALSE)
```
