---
title: "Survey 1 Coding + Scoring"
format: html
editor: visual
---

The first part of this file codes the raw survey responses. The second part scores these into our final variables.

### Load packages, function, and data

```{r}
library(groundhog)

libs <- c("dplyr", "stringr")

groundhog.library(libs, "2023-09-23")

#load functions

source("../../funs/scoringFuns.R")  #this function requires some tidyverse elements

source( "../../funs/beliefcodeFun.R")


```

#### Data

```{r}
survey1 <- read.csv("../../survey_1/data/fake_data/for_scoring_coding/survey1_testdat_sc.csv")
```

# Part 1 - Coding Survey Responses

## Morals & Values Responses

### Individualism and Collectivism

As this uses our standard response scale for agreement we can use our standard scoring function

For the first variable we run the function on survey1, from then on we run it on survey1_scored.

```{r}

#no items are reversed scored so we can just use the same function across all the ic items

#first we select the relevant columns

ic_cols <- colnames(survey1 %>%
  select(starts_with("ic_")))

# now we run the function

survey1_coded <- funScore(survey1, ic_cols, "agreement", FALSE)

```

## Rebelliousness

Rebelliousness uses our standard extent coding scheme, which is also in the standard function

```{r}
reb_cols <- colnames(survey1_coded %>%
  select(starts_with("reb_")))

survey1_coded <- funScore(survey1_coded, reb_cols, "extent", FALSE)
```

## Individual Choice Norms

```{r}
icn_cols <- colnames(survey1_coded %>%
  select(starts_with("icn_")))

survey1_coded <- funScore(survey1_coded, icn_cols, "agreement", FALSE)
```


## Belief Variables

We have a function for these!

```{r}

survey1_coded <- funBeliefCode(survey1_coded)

```

## Write coded data

```{r}

write.csv(survey1_coded, "survey_1_coded_FAKE.csv", row.names = FALSE)
```

# Part 2 - Scoring Survey Variables

Here we score the needed columns into the final variables, and rename the questions to their variable names if needed.

```{r}
# Morals and Values Measures

survey_1_scored <- survey1_coded %>%
  mutate(
    #Individualism & Collectivism Score
    indiv_collectivism = rowMeans(across(starts_with("ic_"), ~ as.numeric(.))), 
    
    #Rebelliousness (Trolling) Score
    rebel_troll = rowMeans(across(c("reb_01", "reb_02", "reb_03", "reb_04"))),
    
    #Rebelliousness (Activism) Score
    rebel_act = rowMeans(across(c("reb_05", "reb_06", "reb_07", "reb_08", "reb_09"))), 
    
    #Rebelliousness (combined) Score
    rebel_all = rowMeans(across(c("rebel_troll", "rebel_act"))),
    
    #Individual Choice Norms Score
    choice_norms = rowMeans(across(starts_with("icn_"), ~ as.numeric(.))),
  )


#Belief Measures

survey_1_scored <- funBeliefCode(survey_1_scored)

# test <- survey_1_scored %>% select(issp_02, agnosticism_bin)  #example test line to check vars *before* select()
```

## Select Variables For Final Data

```{r}

survey_1_vars <- survey_1_scored %>%
  select(1, 2, 3, 4, 68:111, -apx1, -apx2)

colnames(survey_1_vars)

```

## Write Data Files

```{r}
write.csv(survey_1_scored, "survey_1_scored_FAKE.csv", row.names = FALSE)

write.csv(survey_1_vars, "survey_1_vars_FAKE.csv", row.names = FALSE)


```
